\textit{MSF: Modulated Sub-graph Finder}

### 2019-02-20 MSF_Paper_FA.tex
Operation added

\textbf{MSF input}

As input \texttt{MSF} requires the results from
a DGEA in the appropriate file format. So
far the raw output from edgeR~\cite{edgeR} and
DESeq2~\cite{love2014moderated} are supported. Furthermore, a gene network
has to be provided in the format of a directed adjacency list.

@@

@@

\texttt{MSF} is a fast and easy to use tool to find concertedly
modulated sub-graphs in a given network. Its implementation in java enables
its use across many operating systems e.g. linux and windows .

@@

\noindent
Source code: \newline
https://github.com/Modulated-Subgraph-Finder/MSF \newline Software
license: Creative Commons Attribution 4.0 International License

\subsection*{Supplement material}

\noindent
https://github.com/Modulated-Subgraph-Finder/MSF

>>>>

@@

	\textbf{Operation}
	MSF requires Java version 8 and JDK 1.8. The few package dependencies are already been added to the release. MSF runs fast on a standard laptop computer and so it has normal system requirements. To run MSF, the user must provide two text files, one containing the DGEA and the second one containing the interactions in an adjacency format file. Example files and a detailed tutorial to use MSF has been provided on github https://github. com/Modulated-Subgraph-Finder/MSF.

@@

	\texttt{MSF} is a fast and easy to use tool to find concertedly
	modulated sub-graphs in a given network. Its implementation in java enables
	its use across many operating systems e.g. linux and windows. So far the raw output from edgeR~\cite{edgeR} and DESeq2~\cite{love2014moderated} are supported.

@@

	\noindent
	Source code: \newline
	https://github.com/Modulated-Subgraph-Finder/MSF \newline Software
	Software license: MIT license.

	\subsection*{Supplement material}
	Supplementary material is available form GitHub: https://github.com/Modulated-Subgraph-Finder/MSF
